---
title: "EDA"
author: "Arij"
date: "6/23/2022"
output: word_document
---


```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

```

```{r echo=FALSE,include=FALSE,message=FALSE, warning=FALSE}
options(tinytex.verbose = TRUE)
knitr::knit_engines$set(python= reticulate::eng_python)
options(encoding = 'UTF-8')
```

```{r echo=FALSE,include=FALSE,message=FALSE, warning=FALSE}
library(reticulate)
#use_condaenv("C:\\Users\\hp\\Documents\\.conda\\envs\\r-reticulate\\python.exe")
use_python("C:\\Python39\\python.exe")
#reticulate::repl_python()
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(openxlsx)
base=read.xlsx("bilans.xlsx")
attach(base)
```


```{python echo=FALSE, message=FALSE, warning=FALSE}
df1=r.base
df1=df1.drop(columns=['Exercice'])
df1.head()
```


```{python echo=FALSE}
#proportion of missing value in the data 
((df1.isnull().sum()/df1.shape[0])*100).round(4)
```

```{python echo=FALSE}
# drop missing values
df1.dropna(axis=0,inplace=True)
df1.isnull().sum()
```

```{python echo=FALSE}
df1.shape
```



```{python echo=FALSE}
import warnings
warnings.filterwarnings('ignore')
import seaborn as sns
from scipy import stats
import matplotlib.pyplot as plt
plt.figure (figsize=(15,5))
ax=sns.boxplot(data=df1[['X5','R5','X4','R2']], orient="h", palette="Set2")
plt.xticks(size=30)
plt.yticks(size=30)
plt.xlim(-1,6)
ax
```

```{python echo=FALSE}
#plt.figure (figsize=(15,5))
ax = sns.boxplot(data=df1[['X3','R4','X2','R7']], orient="h", palette="Set2")
plt.xticks(size=30)
plt.yticks(size=30)
plt.xlim(-1,1.5)
ax
```


```{python echo=FALSE}
#plt.figure (figsize=(15,5))
ax = sns.boxplot(data=df1[['R3','R1','R6','X1']], orient="h", palette="Set2")
plt.xticks(size=30)
plt.yticks(size=30)
plt.xlim(-4,10)
ax
```


```{python echo=FALSE}
import pandas as pd
import numpy as np
Q1=df1.drop(columns=['Forme_juridique','Secteur','Anciennet\u00e9','statut']).quantile(0.25)
Q3=df1.drop(columns=['Forme_juridique','Secteur','Anciennet\u00e9','statut']).quantile(0.75)
IQR=Q3-Q1
# calculate the outlier cutoff
cut_off = IQR * 1.5
lower,upper = Q1- cut_off, Q3 + cut_off
#print(df.drop(columns=['Forme_juridique','Secteur','Anciennet\u00e9','statut']).columns)
pd.DataFrame(zip(np.transpose(df1.drop(columns=['Forme_juridique','Secteur','Anciennet\u00e9',
'statut']).columns),np.transpose(lower).round(4), np.transpose(upper).round(4)), columns=['variable','lower_limit', 'upper_limit'])
```


```{python echo=FALSE}
((df1.drop(columns=['Forme_juridique','Secteur','Anciennet\u00e9','statut']) < lower) |
 (df1.drop(columns=['Forme_juridique','Secteur','Anciennet\u00e9','statut']) > upper)).sum()
```




```{python echo=FALSE}
df = df1[~((df1 < lower) |(df1 > upper)).any(axis=1)]
((df.drop(columns=['Forme_juridique','Secteur','Anciennet\u00e9','statut']) < lower) |
 (df.drop(columns=['Forme_juridique','Secteur','Anciennet\u00e9','statut']) > upper)).sum()
```
```{python echo=FALSE}
data = df.Secteur.value_counts()
plt.figure(figsize=(10,4))
data.plot.pie(autopct="%.1f%%")
```

```{python echo=FALSE} 
plt.figure (figsize=(15,5))
ax=sns.countplot(x='Forme_juridique',data=df,palette='hls')
for p in ax.patches:
    ax.annotate('{:.1f}'.format(p.get_height()), (p.get_x(), p.get_height()))

```

```{python echo=FALSE} 
plt.figure (figsize=(15,5))
ax=sns.countplot(x='Anciennet\u00e9',data=df,palette='hls')
for p in ax.patches:
    ax.annotate('{:.1f}'.format(p.get_height()), (p.get_x(), p.get_height()))
```

```{python echo=FALSE}
plt.figure (figsize=(15,5))
ax=sns.countplot(x='statut',data=df,palette='hls')
for p in ax.patches:
    ax.annotate('{:.1f}'.format(p.get_height()), (p.get_x(), p.get_height()))
```



### Based on the company's status

```{r echo=FALSE, fig.height=3, fig.width=9, message=FALSE, warning=FALSE}
(ggplot(base2, aes(statut, fill = Forme_juridique))+
  geom_bar(position = "dodge")+xlab("statut")+ylab("Forme_juridique") +
  ggtitle(names(base2[,"Forme_juridique"]))
 +
ggplot(base2, aes(statut, fill = Ancienneté))+
  geom_bar(position = "dodge")+xlab("statut")+ylab("Ancienneté") +
  ggtitle(names(base2[,"Ancienneté"]))
)
```
 


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=4,fig.width=9}
library(GGally)
ggpairs(base.active[,], aes(colour = statut, alpha = 0.4))
```
 
 - The figure above shows several statistical information on the set of variables that make up the Altman Z score:\
  - no linear relationship is detected between the ratios, this is explained by the cloud of points and the correlation matrix
   * a strong correlation between Z and X1, X3 and X5, this is noted from the coefficients of the correlations of these ratios with the Z score and of course their scatter-plots which look like linear functions
   * no other remarkable correlation for the ratios between them.
 
```{r echo=FALSE,message=FALSE, fig.height = 5 , fig.width = 9}
ggpairs(base2[,c((4:10),17)],mapping = aes(colour = statut, alpha = 0.4))

```
- the ratios R1,..,R7 do not show any remarkable correlation between them, so they will all be included in the creation of the model.


